---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

__Note__: This package isn't actually meant to be "serious". It's simply made for STAT547 Homework 09.

# `powers`

This is an R package that gives `sqrt()` friends by providing other power functions.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("cheungamanda/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::square(-3)
powers::reciprocal("2")
powers::areacircle(5)
```

## For Developers

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `quartic`, `reciprocal`. `areacircle`, and `volcyl`.

Cool package, eh? Nah, this silly package was made for class! Don't take it too seriously!
